Human Factors Influencing Visual Statistical Inference

### 2013-06-15 sociology_paper.tex
some typo

Besides United States and India, countries such as Canada, Romania, United Kingdom and Macedonia have more than 10 participants each. The rest of the 70 countries have less than 10 participants. Figure \ref{fig:turker_location_experiment} displays the location of turk workers by each experiment. Notice that For all the ten experiments the locations are similar with some small variations. That may be due to the time of the experiment when it is started. For some experiments India got more participants than United States and for some experiments the numbers just got reversed (\ref{fig:participation_time}). It is also observed in some experiments number of  participants are similar no matter whether the experiment is run on day time or nigh time.

@@

The largest number of participants are from age group 18 to 25 which is the youngest age group in the study. Interestingly we see many participants from older age groups as well. Specially for united states almost all the age groups show uniform participations after age 30 as in Figure \ref{fig:demographic_info}. Notice that fewer people participated from India beyond age 40 compared to united states. Even though total participations from india is larger compared to United States, they are mostly young people who are capable of using internet and computer.

>>>>

Besides United States and India, countries such as Canada, Romania, United Kingdom and Macedonia have more than 10 participants each. The rest of the 70 countries have less than 10 participants. Figure \ref{fig:turker_location_experiment} displays the location of turk workers by each experiment. Notice that For all the ten experiments the locations are similar with some small variations. That may be due to the time of the experiment when it is started. For some experiments India got more participants than United States and for some experiments the numbers just got reversed (\ref{fig:participation_time}). It is also observed in some experiments that number of  participants are similar no matter whether the experiment is run on day time or nigh time.

@@

The largest number of participants are from age group 18 to 25 which is the youngest age group in the study. Interestingly we see many participants from older age groups as well. Specially for united states almost all the age groups show uniform participations after age 30 as in Figure \ref{fig:demographic_info}. Notice that fewer people participated from India beyond age 40 compared to united states. Even though total participations from india is very close to United States, they are mostly young people who are capable of using internet and computer.
